# Clean and prepare

## Settings

We first load the required R packages and set some options for the resulting document.

```{r packages}
#| results: 'hide'
# Packages
library(readxl)
library(imputeTS)
library(naniar)
library(scales)
library(janitor)
library(countrycode)
library(kableExtra)
library(tidyverse)

# Create directory for output files (e.g. plots)
dir.create("output", FALSE)

# Create directory for intermediate data
dir.create("data", FALSE)
```

## Global Burden of Disease

The Global Burden of Disease data were downloaded from <http://ghdx.healthdata.org/gbd-results-tool> on 2021-11-02 to `data-raw/GBD/`. We include those files in the repository as (permitted by the license](http://ghdx.healthdata.org/):

>"Data made available for download by IHME can be used, shared, modified, or built upon by non-commercial users via the Creative Commons Attribution-NonCommercial-NoDerivatives 4.0 International License. Please refer to our terms and conditions for additional details."

We selected the relevant locations, age groups, years, and causes from the data tool as detailed in the manuscript. Next we load all tables (inside downloaded `.zip` files, there may be more than one depending on size of downloaded table) inside the directory.

```{r gbd-data-load}
# Load data files and merge to one table
gbd <- list.files(
  "data-raw/GBD/", 
  pattern = ".zip", full.names = TRUE, recursive = TRUE
) %>% 
  read_csv()
```

We then ensure that the correct variables were downloaded, and then clean this data.

Note we transform the outcome values to proportions so can harmonise easier across all variables

```{r gbd-data-clean}
# Cleaning

# First step is to clean names in all data sets
gbd <- clean_names(gbd)

# Confirm that correct measures were downloaded:
# - prevalence: Total number of cases
# - rate: Total cases per 100,000 population
#   - We convert this to a proportion
# distinct(gbd, measure, metric)
gbd <- select(gbd, -metric, -measure)
gbd <- gbd %>%
  mutate(across(c(val, upper, lower), ~.x/100000))

# Clean cause names
# distinct(gbd, cause)
gbd <- gbd %>% 
  mutate(
    cause = case_when(
      cause == "Anxiety disorders" ~ "Anxiety",
      cause == "Depressive disorders" ~ "Depression",
      cause == "Self-harm" ~ "Selfharm"
    )
  )

# Harmonise variable names with other datasets
gbd <- gbd %>% 
  rename(country = location)

# The outcomes values are model predictions and come with lower and upper CI limits (2.5 and 97.5 %iles of their posterior distributions).We convert those to normal approximate standard errors.
gbd <- gbd %>% 
  mutate(se = (upper-lower) / (1.96*2)) %>%
  select(-c(upper, lower))
```

Then we need to harmonise to country names (always somewhat idiosyncratic) to a common metric. We use the short English names from the UNICODE CLDR project as provided by `countrycode::countryname()`. There is a harmonised name for each GBD country, and 27 country names are harmonised.

```{r gbd-harmonise-countries}
# Check what names were changed and if any don't have harmonised counterpart
gbd %>%
  distinct(country) %>% 
  arrange(country) %>%
  mutate(
    country_harmonised = countryname(country, destination = "cldr.short.en")
  ) %>% 
  filter(country != country_harmonised | is.na(country_harmonised)) %>% 
  kbl() %>% 
  kable_minimal(full_width = FALSE) %>% 
  scroll_box(width = "500px", height = "400px")
# Harmonise old names after verifying above that none are dropped
gbd <- gbd %>% 
  mutate(country = countryname(country, destination = "cldr.short.en"))
```

## Gallup World Poll

GWP cleaning goes here.

## International Telecommunication Union

We first download the data files from the ITU website (in November 2021). Note that new versions may be posted subsequent to this, in which case the URLs would change and should then be changed here too to update the analyses with latest data.

```{r itu-download}
# Download data sets from the ITU website if not yet downloaded
if (!file.exists("data-raw/ITU/PercentIndividualsUsingInternet.xlsx")) {
  dir.create("data-raw/ITU")
  download.file(
    "https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2021/PercentIndividualsUsingInternet_Nov2021.xlsx", 
    "data-raw/ITU/PercentIndividualsUsingInternet.xlsx"
  )
  download.file(
    "https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2021/July/FixedBroadbandSubscriptions_2000-2020.xlsx",
    "data-raw/ITU/FixedBroadbandSubscriptions_2000-2020.xlsx"
  )
  download.file(
    "https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2021/July/MobileBroadbandSubscriptions_2007-2020.xlsx",
    "data-raw/ITU/MobileBroadbandSubscriptions_2007-2020.xlsx"
  )
}
```

We then read and reshape the ITU data

```{r itu-clean}
# Read and reshape fixed broadband data
itu_fixed <- read_xlsx(
  "data-raw/ITU/FixedBroadbandSubscriptions_2000-2020.xlsx", 
  sheet = 2,
  col_types = "text"
) %>% 
  pivot_longer(-c(Indicator, Country)) %>% 
  separate(name, into = c("year", "variable")) %>% 
  pivot_wider(names_from = variable) %>% 
  mutate(fixed = as.numeric(value)) %>% 
  select(country = Country, year, fixed)

# Read and reshape mobile broadband data
itu_mobile <- read_xlsx(
  "data-raw/ITU/MobileBroadbandSubscriptions_2007-2020.xlsx", 
  sheet = 2,
  col_types = "text"
) %>% 
  pivot_longer(-c(Indicator, Country)) %>% 
  separate(name, into = c("year", "variable")) %>% 
  pivot_wider(names_from = variable) %>% 
  mutate(mobile = as.numeric(value)) %>% 
  select(country = Country, year, mobile)

# Percent using internet
itu_percent <- read_xlsx(
  "data-raw/ITU/PercentIndividualsUsingInternet.xlsx",
  col_types = "text"
) %>% 
  pivot_longer(-c(Indicator, Country)) %>% 
  separate(name, into = c("year", "variable")) %>% 
  pivot_wider(names_from = variable) %>% 
  mutate(internet = as.numeric(value)) %>% 
  select(country = Country, year, internet)

# Merge to one table in wide format (oldest on left to include all years)
itu <- reduce(list(itu_percent, itu_fixed, itu_mobile), left_join)

# values (1-100) to proportions (0-1) and years to numbers
itu <- itu %>% 
  mutate(across(c(internet, fixed, mobile), function(x) x/100)) %>% 
  mutate(year = as.numeric(year))

# Drop tables
rm(itu_fixed, itu_mobile, itu_percent)
```

Then harmonise country names as above, and drop countries that don't exist in outcomes.

```{r itu-harmonise-countries}
# Check what names were changed and if any don't have harmonised counterpart
itu %>%
  distinct(country) %>% 
  arrange(country) %>%
  mutate(
    country_harmonised = countryname(country, destination = "cldr.short.en")
  ) %>% 
  filter(country != country_harmonised | is.na(country_harmonised)) %>% 
  kbl() %>% 
  kable_minimal(full_width = FALSE) %>% 
  scroll_box(width = "500px", height = "400px")

# Harmonise old names after verifying above that none are dropped
itu <- itu %>% 
  mutate(country = countryname(country, destination = "cldr.short.en"))

# These countries don't exist in outcomes
itu %>%
  distinct(country) %>% 
  anti_join(distinct(gbd, country)) %>% 
  kbl() %>% 
  kable_minimal(full_width = FALSE) %>% 
  scroll_box(width = "500px", height = "400px")

# Drop them
itu <- itu %>% 
  filter(country %in% unique(gbd$country))
```

### Missingness

Remove countries with no observations

```{r}
itu <- itu %>% 
  group_by(country) %>% 
  mutate(nobs = sum(!is.na(internet))) %>% 
  ungroup() %>% 
  filter(nobs > 0) %>% 
  select(-nobs)
```

We then impute missing values to the internet adoption timeseries. We use linear interpolation to fill missing intermediate values, but do not extrapolate before or after the first and last values of each country.

```{r itu-impute}
# Reshape to easily impute all variables
itu_long <- itu %>%
  pivot_longer(c(internet, fixed, mobile))

# Impute by country and variable
itu_long <- itu_long %>%
  group_by(country, name) %>% 
  # Find first and last year with this variable in each country
  # so as to prevent extrapolation
  mutate(
    min_year = year[min(which(!is.na(value)))],
    max_year = year[max(which(!is.na(value)))]
  ) %>%
  # Interpolate values linearly
  # use possibly() to avoid errors for countries with no data
  mutate(
    across(
      value, 
      .fns = list(
        i = possibly(
          function(x) na_interpolation(x, maxgap = Inf), 
          otherwise = NaN
        )
      )
    )
  ) %>% 
  # Take out projected (non-intermediate) imputed values
  mutate(
    value_i = if_else(
      between(year, unique(min_year), unique(max_year)), 
      value_i, 
      NaN
    )
  ) %>% 
  ungroup() %>% 
  select(-min_year, -max_year)
```

Here is a summary of how many values were imputed

```{r}
itu_long %>%   
  group_by(name) %>% 
  mutate(min_year = if_else(name == "mobile", 2007, 2000)) %>% 
  summarise(
    n_miss_orig = sum(is.na(value) & year >= min_year),
    p_miss_orig = percent(n_miss_orig / sum(year >= min_year), .1),
    n_miss_imp = sum(is.na(value_i) & year >= min_year),
    p_miss_imp = percent(n_miss_imp / sum(year >= min_year), .1),
    imputed = n_miss_orig - n_miss_imp
  )
```

We then replace the original values with the imputed ones

```{r}
itu <- itu_long %>% 
  mutate(value = value_i) %>% 
  select(-value_i) %>% 
  pivot_wider()
rm(itu_long)
```

## Covariates

Human Development Index



## GLOBE regions

We group the countries into GLOBE regions in order to have a higher level of grouping at which the analyses can be summarised. This allows us to eg. present figures and tables per region, instead of overwhelmingly by country, and also provides an upper level for the multilevel models. We use the extended GLOBE regions following Jebb et al. (2020), and had to manually add labels to some countries that were not grouped in those studies.

```{r}
regions <- read_csv(
  "data-raw/Regions/GLOBE-regions-from-Jebb-et-al-2020.csv"
) %>% 
  # Jebb et al used * to indicate deviance from GLOBE, remove
  mutate(country = str_remove_all(country, "\\*")) %>% 
  # Standardize country names
  # This drops Nagorno-Karabakh Republic
  mutate(country = countryname(country)) %>% 
  drop_na(country)

# This also combined Swaziland and (Eswatini) to Eswatini, and Northern- and Cyprus. Therefore we just take the distinct country & region.
regions <- distinct(regions, region, country)

# Countries in our dataset not present in region data
filter(
  distinct(gbd, country), 
  !(country %in% unique(regions$country))
) %>% 
  arrange(country) %>% 
  write_csv("data-raw/Regions/GBD-countries-without-region.csv")

# I then filled missing regions in Jebb et al and extended GLOBE referenced therein

# Load our manually filled region data
regions_filled <- read_csv(
  "data-raw/Regions/GBD-countries-without-region-filled.csv"
) 
```

We then combine all the region tables, clean region names, and join to our data

```{r}
# Combine Jebb et al GLOBE regions and our manually added ones
regions <- regions %>% 
  bind_rows(
    regions_filled %>% 
      mutate(Note = "Filled")
  ) %>% 
  arrange(region, country)

# Shorter name for plots
regions <- regions %>% 
  mutate(region = if_else(region=="Sub-Sahara Africa", "Africa", region))

# Format regions to factors and use line breaks instead of spaces
regions$region <- factor(regions$region)
levels(regions$region) <- str_replace_all(levels(regions$region), " ", "\n")

# Display table of regions and countries
regions %>% 
  kbl(caption = "All countries and regions.") %>% 
  kable_minimal(full_width = FALSE) %>% 
  scroll_box(width = "500px", height = "400px")

regions <- select(regions, -Note)
```

## Join tables

Here, we join the ITU table to the GBD table. Note this appropriately duplicates the country-specific predictor values to the demographic groups within each country. We then create a table specific to young people. 

We also join regions to the data.

```{r}
# Add regions to data tables
itu <- left_join(itu, regions)
gbd <- left_join(gbd, regions)
```

Our primary analysis is about young people but we also look at older groups for supplemental comparison, so we split data here.

```{r}
gbd_all <- gbd
gbd <- gbd %>% 
  filter(age %in% c("10 to 14", "15 to 19", "20 to 24"))
```

## Save tables

We then save the tables for later use in `data/`.

```{r}
write_rds(gbd, "data/gbd.rds")
write_rds(gbd_all, "data/gbd_all_ages.rds")
write_rds(itu, "data/itu.rds")
```
